SMT-COMP 2022\\ 17th International Satisfiability Modulo Theory Competition

### 2023-01-03 2022/slides/flocOlympics/slides.tex
missing slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2022 - Presentation on SMT-Workshop
%                   virtual conference in "Los Angeles"
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2022\\
17th International Satisfiability Modulo Theory Competition}
\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
\date{Aug 11, 2022}

@@

@@

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Non-incremental}
        391\,363 instances {\small (+9680)}\\
        with 1 query each \\
        in 81 logics {\small (+2)}.
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Incremental}
        43\,285 instances {\small (+1)}\\
        with 33\,998\,935 queries {\small (+141)} \\
        in 39 logics.
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}
  \pause
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Non-incremental}
        \only<2>{206\,932 instances}\only<3>{\textcolor{red}{206\,932}
          instances\\
          \textcolor{red}{We mistakenly ignored 9466 new benchmarks}
        }
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Incremental}
        22\,300 instances
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}

@@

\begin{frame}[fragile]{SMT-COMP Tracks (traditional)}
  \emph{Single Query (SQ) Track}
  \begin{itemize}
  \item Determine satisfiability of one problem
  \item Solver answers sat/unsat/unknown
  \end{itemize}
  \medskip

@@

\medskip
\pause
  \emph{This year} the sat/unsat results from sound solvers in SQ were used to
  include benchmarks on the MV, UC and PE tracks.

@@

  \bigskip
  Six new solvers participated:
  \begin{itemize}
  \item NRA-LS   {\footnotesize (Liu et al.)}
  \item OSTRICH {\footnotesize (Chen et al.)}
  \item Yices-ismt {\footnotesize (Jia et al.)}
  \item Z3++ {\footnotesize (Cai et al.)}
  \item solsmt {\footnotesize (Reitwiessner and Soos)}
  \end{itemize}

@@

\section{Solver Presentation}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-bitwuzla.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-colibri.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-cvc5.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-cvc5-cloud.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-nra-ls.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-opensmt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-ostrich.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-smtinterpol.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-smtrat.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-solsmt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-stp.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-verit.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices-ismt.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-yices-qs.pdf}}
\end{frame}
}

{
\begin{frame}
  \vspace*{-1pt}%
  \noindent\makebox[\textwidth]{%
    \includegraphics[height=\paperheight]{slide-z3pp.pdf}}
\end{frame}
}

{
  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
      \item Q3B
      \vitem SMT-RAT
      \vitem SMTS
      \vitem UltimateEliminatior+MathSAT
      \vitem Vampire
      \vitem Z3str4
    \end{itemize}
  \end{frame}
}

@@

  Submitted by organisers
  \begin{itemize}
  \item z3-4.8.17
  \item MathSAT 5.6.8
  \item Best solvers, per division, from previous years (23 Solvers)
  \end{itemize}
  \bigskip

@@

\begin{frame}{Division Winners}
  \pause
  \emph{Single Query, sequential score}
  \begin{itemize}
  \item \emph{Bitwuzla}: {\small FPArith, QF\_Bitvec, QF\_Equality+Bitvec, QF\_FPArith}

  \item \emph{cvc5}: \begin{minipage}{.8\textwidth}\raggedright \tiny Arith,
    Bitvec, Equality, Equality+LinearArith, Equality+MachineArith,
    Equality+NonLinearArith, QF\_Datatypes, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith, QF\_NonLinearRealArith, QF\_Strings\end{minipage}

  \item \emph{OpenSMT}: {\small QF\_LinearIntArith}

  \item \emph{SMTInterpol}: {\small QF\_Equality+LinearArith}

  \item \emph{Yices2}: {\small QF\_Equality, QF\_LinearRealArith}
  \end{itemize}

  \medskip

  \pause
  \emph{Unsat Core}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith, Equality+MachineArith,Equality+NonLinearArith,Equality(Seq), QF\_Datatypes
\item \emph{Vampire}: Equality(Par)
\item \emph{Bitwuzla}: QF\_EqualityBitvec, QF\_FPArith
\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+LinearArith, QF\_Equality, QF\_LinearIntArith, QF\_LinearRealArith
\item \emph{SMTInterpol}: QF\_Equality+NonLinearArith
\item \emph{UltimateEliminator+MathSAT}: FPArith

  \end{itemize}

@@

\begin{frame}{Division Winners}
  \emph{Incremental}
  \begin{itemize}
\item \emph{cvc5}: Arith, Bitvec, Equality+LinearArith,EqualityNonLinearArith,Equality
\item \emph{UltimateEliminator+MathSAT}: Equality+MachineArith
\item \emph{Bitwuzla}: FPArith, QF\_FPArith
\item \emph{Yices2}: QF\_Bitvec, QF\_Equality+Bitvec, QF\_Equality, QF\_LinearIntArith
\item \emph{SMTInterpol}: QF\_Equality+LinearArith, QF\_Equality+NonLinearArith, QF\_NonLinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith
  \end{itemize}
  \medskip

  \pause
  \emph{Model Validation (competitive only)}
  \begin{itemize}
\item \emph{Bitwuzla}: QF\_Bitvec, QF\_Equality+Bitvec,
\item \emph{smtinterpol}: QF\_Equality+LinearArith
\item \emph{Yices2}: QF\_Equality
\item \emph{Z3++}: QF\_LinearIntArith
\item \emph{OpenSMT}: QF\_LinearRealArith

\item experimental: QF\_FPArith : Bitwuzla, cvc5

  \end{itemize}
\end{frame}

\begin{frame}{Largest contribution}
  \begin{tabular}{r|c@{}lc@{}lc@{}l}
    &\textcolor{gold}{\textbf{1st Place}} &&
    \textcolor{silver}{\textbf{2nd Place}} &&
    \textcolor{bronze}{\textbf{3rd Place}}\\
    \hline
    \emph{Single Query}\\
    seq & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    par & cvc5&{\tiny(Eq+MA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    sat & cvc5&{\tiny(Eq+LA)} & YicesQS&{\tiny(Arith)} & Bitwuzla&{\tiny(FPArith)} \\
    unsat & cvc5&{\tiny(Eq+MA)} & Z3++&{\tiny(QF\_NonLIA)} & OSTRICH&{\tiny(QF\_Strings)}\\
    24 &  Vampire&{\tiny(Eq+NA)} & Vampire&{\tiny(Equality)} & Yices2&{\tiny(QF\_LinIA)}\\[3pt]
    \pause
    \emph{Incremental}\\
    par & cvc5&{\tiny(Eq+NA)} &Yices2&{\tiny(QF\_Eq+LA)}
    &SMTInterpol&{\tiny(QF\_Eq+NA)}\\[3pt]
    \pause

    \emph{Unsat Core}\\
    seq & cvc5&{\tiny(Eq+LA)} &
    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\

    par &  cvc5&{\tiny(Eq+NA)}&
    Bitwuzla&{\tiny(QF\_Eq+Bitvec)}\\
\\[3pt]
    \pause
    \emph{Model Validation}\\
    seq &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
    par &  Z3++&{\tiny(QF\_LinIA)} & Bitwuzla&{\tiny(QF\_Bitvec)}
        & smtinterpol&{\tiny(QF\_Eq+LIA)}\\
  \end{tabular}
\end{frame}

\begin{frame}{Biggest Lead}
  \begin{tabular}{r|c@{}lc@{}lc@{}l}
    &\textcolor{gold}{\textbf{1st Place}} &&
    \textcolor{silver}{\textbf{2nd Place}} &&
    \textcolor{bronze}{\textbf{3rd Place}}\\
    \hline
    \emph{Single Query}\\
    seq & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
    par & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Yices2&{\tiny(QF\_LinRA)} \\
    sat & cvc5&{\tiny(QF\_DT)} & Bitwuzla&{\tiny(FPArith)} & Z3++&{\tiny(QF\_NonRA)} \\
    unsat & cvc5&{\tiny(QF\_DT)} & Z3++&{\tiny(QF\_NonIA)} & Bitwuzla&{\tiny(FPArith)} \\
    24 &  cvc5&{\tiny(Eq+MA)} & smtinterpol&{\tiny(QF\_DT)} & Vampire&{\tiny(Equality)}\\[3pt]
    \pause
    \emph{Incremental}\\
    par & SMTInterpol&{\tiny(QF\_NIA)}
    &Yices2&{\tiny(QF\_LinIA)} & cvc5&{\tiny(Eq+NonLA)} \\[3pt]
    \pause
    \emph{Unsat Core}\\
    seq & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
    par & cvc5&{\tiny(Eq+MA)} &    Yices2&{\tiny(QF\_Eq+LA)} &    smtinterpol&{\tiny(QF\_Eq+NA)} \\
    \pause
    \emph{Model Validation}\\
    seq &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
    par &  Z3++&{\tiny(QF\_LinIA)} & smtinterpol&{\tiny(QF\_LinA)}        & OpenSMT&{\tiny(QF\_LinRA)} \\
  \end{tabular}
\end{frame}

\begin{frame}{Checking Disagreements}

  \begin{itemize}
  \item  111\,451 instances of 391\,363 have no status

  \vitem Only 18 benchmarks with disagreements (AUFDTLIA, QF\_NIA)

  \vitem We manually resolved the disagreements
  \begin{itemize}
    \item Authors confirmed solver unsoundness
    \item Sound solvers agreed on result
  \end{itemize}

  \vitem We had only three solvers with soundness issues: SMTIinterpol, Z3++,
  yices-ismt
  \begin{itemize}
    \item Down from 10 last year
    \pause
    {\tiny (but note that this may be because of our issue with ignoring most of the
    new benchmarks in the selection)}

  \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Plans for SMT-COMP 2022}
  \begin{itemize}
    \item Move to Dolmen as single model validator

      \vitem Dolmen worked well in QF\_FP (minor issue with empty output, simple
      to fix)
      \vitem pysmt timed out in two cases (locally with more time one of them
      succeeded)
      \vitem pysmt could not understand the model in 9 cases
      \vitem Dolmen is easy to extend to new theories
      \vitem Easy to integrate with correct-by-construction code extracted from
      Coq
      \vitem Should be more efficient for handling function call

  \end{itemize}

@@

\begin{frame}{Plans for SMT-COMP 2022}
  \begin{itemize}
    \item Proof \textit{validation} track

      \vitem Hopefully proof exhibition this year will help

      \vitem We have to analyze the data still
      \begin{itemize}
        \item Job only finished last week (took 18 days to run)
        \item 830gb
      \end{itemize}

  \end{itemize}

@@

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2022:
  \begin{itemize}
  \item Haniel Barbosa
  \item Jochen Hoenicke
  \item Fran\c{c}ois Bobot
  \end{itemize}

  Both Haniel and Jochen have been organizers for three-years. One of them
  should be replaced.
  \bigskip

  We need a successor for next year's competition.
  Contact us if you would like to volunteer!
\end{frame}

\begin{frame}{Acknowledgements}
  \begin{itemize}
    \item \emph{Andrea Micheli}: pysmt
    \item \emph{Guillaume Bury}: Model Validator
    \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
    \item \emph{Aaron Stump}: StarExec support
    \item \emph{Mike Whalen and team}: Cloud/Parallel Track
  \end{itemize}
  \bigskip

  \begin{columns}
    \begin{column}{.3\textwidth}
      \includegraphics[width=\textwidth]{starlogo}
    \end{column}
    \begin{column}{.17\textwidth}
      \includegraphics[width=\textwidth]{powered-by-aws}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[shrink=0.95]{Benchmark contributors}
  In 2022 \emph{new benchmarks} were contributed by:

  \small
  \begin{itemize}
    \item  Alex Coffin
    \item  Alex Ozdemir
    \item  Ali Uncu, James Davenport and Matthew England
    \item  Bohan Li
    \item  Elizabeth Polgreen
    \item  Fuqi Jia
    \item  Johann-Tobias Aaron and Raphael Schäg
    \item  Matthew England and Miguel Del Rio Almajano
    \item  Nicolas Amat
    \item  Yannick Moy
    \item  Yoni Zohar
  \end{itemize}
\end{frame}

@@

  \begin{center}
    \Large\emph{Thanks}
  \end{center}

  \begin{center}
    to all participants
  \end{center}

  \bigskip
  \pause

  \begin{center}
    and to you for listening
  \end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   SMT-COMP 2021 - Presentation on SMT-Workshop
%                   virtual conference in "Los Angeles"
%
%   1 hour
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Titel, Autor und Datum des Vortrags:
\title{SMT-COMP 2022\\
17th International Satisfiability Modulo Theory Competition}
\author{\emph{Haniel Barbosa} \and Jochen Hoenicke \and Fran\c{c}ois Bobot}
\date{Aug 9, 2022\\[2ex]      \includegraphics[width=\textwidth]{floc}
}

@@

\newcommand{\yell}[1]{{\color{red} [#1]}}

% 2952bfff
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}

@@

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Non-incremental}
        391\,363 instances\\
        with 1 query each \\
        in 81 logics.
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Incremental}
        43\,285 instances\\
        with 33\,998\,935 queries \\
        in 39 logics.
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}
  \pause
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Non-incremental}
        206\,932 instances
      \end{block}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{block}{Selected Incremental}
        22\,300 instances
      \end{block}
    \end{column}
    \begin{column}{0.08\textwidth}
    \end{column}
  \end{columns}

@@

\begin{frame}[fragile]{SMT-COMP Tracks (traditional)}
  \emph{Single Query Track}
  \begin{itemize}
  \item Determine satisfiability of one problem
  \item Solver answers sat/unsat/unknown
  \end{itemize}
  \medskip

@@

@@

  \bigskip
  Six new solvers participated:
  \begin{itemize}
  \item NRA-LS   {\footnotesize (Liu et al.)}
  \item OSTRICH {\footnotesize (Chen et al.)}
  \item Q3B {\footnotesize (Jon\'a\v{s} and Strej\v{c}ek)}
  \item Yices-ismt {\footnotesize (Jia et al.)}
  \item Z3++ {\footnotesize (Cai et al.)}
  \item solsmt {\footnotesize (Reitwiessner and Soos)}
  \end{itemize}

@@

@@

  Submitted by organisers
  \begin{itemize}
  \item z3-4.8.17
  \item MathSAT 5.6.8
  \item Division winners from previous years (23 Solvers)
  \end{itemize}
  \bigskip

@@

\begin{frame}{FLoC Medalists}

  \begin{columns}
    \begin{column}{0.6\textwidth}

  \Large 8 medals
  \begin{itemize}
    \bigskip
    \vitem Biggest Lead
    \begin{itemize}
      \item Single Query: Gold and Silver
      \item Model Validation: Gold
      \item Incremental: Gold
    \end{itemize}
    \bigskip

    \vitem Largest Contribution
    \begin{itemize}
      \item Single Query: Gold and Silver
      \item Model Validation: Gold
      \item Incremental: Gold
    \end{itemize}
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}\\
    \includegraphics[width=.3\textwidth]{medalsilver}
    \includegraphics[width=.3\textwidth]{medalsilver}
  \end{center}
\end{column}
\end{columns}

@@

\begin{frame}{FLoC Medalists}

  \begin{columns}
    \begin{column}{0.6\textwidth}

  \Large cvc5 wins three gold medals:
  \begin{itemize}
    \bigskip
    \vitem Single Query, Biggest Lead
    \bigskip

    \vitem Single Query, Largest Contribution
    \bigskip

    \vitem Incremental, Largest Contribution
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}
  \end{center}
\end{column}
\end{columns}

@@

\begin{frame}{FLoC Medalists}

  \begin{columns}
    \begin{column}{0.6\textwidth}

  \Large Z3++ wins two gold medals:
  \begin{itemize}
    \bigskip
    \vitem Model Validation, Biggest Lead
    \bigskip

    \vitem Model Validation, Largest Contribution
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=.3\textwidth]{medalgold}
    \includegraphics[width=.3\textwidth]{medalgold}
  \end{center}
\end{column}
\end{columns}

@@

\begin{frame}{FLoC Medalists}

  \begin{columns}
    \begin{column}{0.6\textwidth}

  \Large SMTInterpol wins one gold medal:
  \begin{itemize}
    \bigskip
    \vitem Incremental, Biggest Lead
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=.3\textwidth]{medalgold}
  \end{center}
\end{column}
\end{columns}

\begin{frame}{FLoC Medalists}

  \begin{columns}
    \begin{column}{0.6\textwidth}

  \Large Bitwuzla wins one silver medal:
  \begin{itemize}
    \bigskip
    \vitem Single Query, Biggest Lead
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=.3\textwidth]{medalsilver}
  \end{center}
\end{column}
\end{columns}

\begin{frame}{FLoC Medalists}

  \begin{columns}
    \begin{column}{0.6\textwidth}

  \Large YicesQS wins one silver medal:
  \begin{itemize}
    \bigskip
    \vitem Single Query, Largest Contribution
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=.3\textwidth]{medalsilver}
  \end{center}
\end{column}
\end{columns}

@@

  \begin{center}
    \Large For full results please come to the SMT workshop Thursday 4pm.
  \end{center}
